Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Add keyword
Minor Wosnik edits in introduction

% Keywords: add 3 to 10 keywords
\keyword{Reynolds number; cross-flow turbine; turbine performance; marine
hydrokinetic energy; wind energy; VAWT}

@@

The wake of a 2-D cross-flow turbine in the dynamic stall regime has been
studied via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and
in 3-D with particle image velocimetry (PIV) by Fujisawa and Shibuya
\cite{Fujisawa2001}. However, both of these studies were performed at very low
Reynolds numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine at optimal
tip speed ratio in a wind tunnel using stereo PIV at an approximate blade chord
Reynolds number $Re_c = 1.7 \times 10^5$; very close to the $Re$-independence
criteria reported in \cite{Bachant2014}, though it was not confirmed if this was
indeed a $Re$-independent state. The two lower $Re$ experiments tended to focus
on the effects of dynamic stall, whereas the higher $Re$ experiment mostly
concerned the mean velocity and tip vortex effects. Despite their value
elucidating the complex wake dynamics of cross-flow turbines, these studies
motivate the systematic investigation of scale effects undertaken here.

@@

Vertical-axis wind turbine array field experiments have revealed that
accelerated wake recovery allows for closer spacing when compared with
conventional axial-flow propeller-type turbines \cite{Dabiri2011, Kinzel2012}.
It was observed experimentally that a high solidity vertical-axis cross-flow
turbine's near-wake produces a unique vertical mean velocity field---generated
by blade tip vortex shedding---the advection by which is the largest contributor
to streamwise momentum and energy transport or recovery \cite{Bachant2015-JoT}.
In this study we seek to replicate those same momentum and energy balance
considerations at multiple Reynolds numbers, to examine the implications on how
small scale, i.e., low Reynolds number experiments may be used to study flows in
turbine arrays.

>>>>

% Keywords: add 3 to 10 keywords
\keyword{Reynolds number; cross-flow turbine; turbine performance; marine
hydrokinetic energy; wind energy; VAWT; scale model}

@@

The wake of a 2-D cross-flow turbine in the dynamic stall regime has been
studied via laser Doppler velocimetry by Brochier et al. \cite{Brochier1986} and
in 3-D with particle image velocimetry (PIV) by Fujisawa and Shibuya
\cite{Fujisawa2001}. However, both of these studies were performed at very low
Reynolds numbers---$Re_D = 10^4$ and $10^3$, respectively. Tescione et al.
\cite{Tescione2014} studied the wake of a vertical-axis wind turbine at optimal
tip speed ratio in a wind tunnel using stereo PIV at an approximate blade chord
Reynolds number $Re_c = 1.7 \times 10^5$; very close to the $Re$-independence
criteria reported in \cite{Bachant2014}, though it was not confirmed if this was
indeed a $Re$-independent state. The two lower $Re$ experiments tended to focus
on the effects of dynamic stall, whereas the higher $Re$ experiment mostly
concerned the mean velocity and tip vortex effects. Whereas the value of these
studies was in elucidating the complex wake dynamics of cross-flow turbines,
they also motivated the more systematic investigation of scale effects
undertaken here.

@@

Vertical-axis wind turbine array field experiments have revealed that improved
wake recovery allows for closer spacing when compared to conventional axial-flow
propeller-type turbines \cite{Dabiri2011, Kinzel2012}. It was observed
experimentally that a high solidity vertical-axis cross-flow turbine's near-wake
produces a unique vertical mean velocity field---generated by blade tip vortex
shedding---the advection by which is the largest contributor to streamwise
momentum and energy transport or recovery \cite{Bachant2015-JoT}. In this study
we seek to replicate those same momentum and energy balance considerations at
multiple Reynolds numbers, to examine the implications on how scaled, i.e., low
Reynolds number experiments may be used to study flows in turbine arrays.
